---
title: "Question5_D_E"
author: "Matt Rega"
date: "December 3, 2017"
output: html_document
---

#Relationship between Income and Age
```{r}

library(ggplot2)

#Scatterplot
ggplot(subset(Procrastination,!is.na(AnnualIncome)&!is.na(Age)&!is.na(Gender)),aes(x=Age,y=AnnualIncome,shape=Gender,color=Gender))+geom_point()+xlab("Age")+ylab("Annual Income in Dollars")+ggtitle("Annual Income vs Age")+theme(plot.title = element_text(hjust=0.5))

#create smaller data set for regression model
income_age_data<-data.frame(Procrastination$Age,Procrastination$Gender,Procrastination$AnnualIncome)
names(income_age_data)<-c("Age","Gender","Income")
income_age_data$male<-ifelse(income_age_data$Gender=="Male",1,0)

#correlation of age and income
cor.test(Procrastination$Age,Procrastination$AnnualIncome,method="pearson",use = "complete.obs")

#create linear regression model using just age 
income_age_model<-lm(Income~Age,data=income_age_data)
summary(income_age_model)

#create linear regression model using age and gender
income_age_model2<-lm(Income~male+Age,data=income_age_data)
summary(income_age_model2)

```

	Overall there is a statistically significant linear relationship between a person's age and their annual income. The scatter plot is a little challenging to read because there are so many observations with the same age and income but the correlation test can be used to interpret this relationship. The correlation coefficient is 0.3723 with a p-value of less than 0.05. This means that the two variable are linear correlated and since 0.3723 is positive they are positively correlated. As age increases so does annual income. This is not a particularly strong correlation but there is one present.
	This relationship is further supported by looking at a simple linear regression occasion using age to predict annual income. The coefficient for age is 1498.12 which means that for every one year increase in age a person's annual income is predicted to increase by $1,498.12. Again this is an increase which supports the positive linear correlation found using the correlation test.
	If we add gender into the regression equation the coefficient for age drops to 1458.2. This means that for every one year increase in age a person's annual income is predicted to increase $1,458.2. The coefficient for the male indicator variable, this variable has a value of 1 if the observation is a male, is 15859. This means that if a male and female are the same age it is predicted that the male would have an annual income that is $15,859 higher than the female.  

#Relationship between Life Satisfaction and Human Development Index
```{r}
#scatterplot life satisfaction vs hdi
ggplot(Procrastination,aes(x=Procrastination$`2016_Est_HDI`,y=SWLSPMean,shape=Gender,color=Gender))+geom_point()+xlab("Human Development Rating")+ylab("Life Statisfaction Rating (1-5(Highest))")+ggtitle("Life Statisfaction vs Human Development Rating")+theme(plot.title = element_text(hjust=0.5))+scale_x_discrete(breaks=pretty(Procrastination$`2016_Est_HDI`,n=75))+coord_flip()

#create smaller data set for regression model
ls_hdi_data<-data.frame(as.numeric(Procrastination$`2016_Est_HDI`),Procrastination$Gender,Procrastination$SWLSPMean)
names(ls_hdi_data)<-c("HDI","Gender","Life_Satisfaction")
ls_hdi_data$male<-ifelse(ls_hdi_data$Gender=="Male",1,0)

#correlation of HDI and Life satisfaction
cor.test(as.numeric(Procrastination$`2016_Est_HDI`),Procrastination$SWLSPMean,method="pearson",use = "complete.obs")

#create linear regression model using just HDI to predict life satisfaction
ls_hdi_model<-lm(Life_Satisfaction~HDI,data=ls_hdi_data)
summary(ls_hdi_model)

#Create linear regression model using HDI and gender to predict life satisfaction
ls_hdi_model2<-lm(Life_Satisfaction~HDI+male,data=ls_hdi_data)
summary(ls_hdi_model2)

```
  Again the scatterplot is difficult to read due to the high number of similar observations so we will look at the statistical tests. The correlation test returns a correlation coefficient of 0.0395 with a p-value of 0.01. This means that human development index and life satisfaction do have a statistically significant linear relationship but it is very weak. The correlation coefficient is only 0.03 so the relation is not strong. It is positive though which means that as the human development index of the country goes up the life satisfaction of the observation increases as well, even if it is only slightly.
	This again is supported by a linear regression model. First looking at only using the human development index to predict an observations predicted life satisfaction. The coefficient for HDI is 0.6855 which means for a 0.1 unit increase in HDI an observations life satisfaction only increases by 0.06855. We use 0.1 increase for HDI because it is measured on a scale from 0 to 1 so a 1 unit increase is extremely unlikely and a 0.1 unit increase is much more plausible. Life satisfaction is measured on a scale from 1 to 5 so a 0.06 unit increase is not nothing but it is not a large increase. This supports the correlation coefficient being very weak.
	If we include gender in the regression equation, again with an indicator variable that equals 1 if the observation is a male, the coefficient for HDI drops to 0.51255 which means that now a 0.1 unit increase in HDI results in a predicted increase of 0.05 in life satisfaction. The coefficient for the male indicator variable is -0.235. This means that if a male and female lived in a country with the same HDI the male would have a life expectance 0.235 units lower than the female. This suggests that men are on average less satisfied than females.

#Relationship between life satisfaction and hdi category
```{r}
#Create a barplot of life statisfaction and hid category
hdi_ls_mean<-aggregate(Procrastination$SWLSPMean,list(Procrastination$HDI_Category),mean)
names(hdi_ls_mean)<-c("Group","Mean_Life_Satisfaction")

ggplot(hdi_ls_mean,aes(x=reorder(Group,Mean_Life_Satisfaction),y=Mean_Life_Satisfaction))+geom_bar(stat="identity",fill="#009E73")+ggtitle("Mean Life Satisfaction by HDI Category")+theme(plot.title = element_text(hjust=0.5))+xlab("HDI Category")+ylab("Mean Life Satisfaction")

#Anova test comparing the four groups
anova_model<-aov(Procrastination$SWLSPMean~Procrastination$HDI_Category)
summary(model)
TukeyHSD(model)
```
  Looking at the bar graph there does seem to be an increase in life satisfaction as the HDI category moves to a higher quality of life. However if an ANOVA test is run on the different groups this says the opposite. The ANOVA test has a p-value of 0.128 which means that the four groups do not have statistically significant different life satisfaction ratings. So while it does look like there is an increase in life satisfaction this increase is not statistically significant.
  
#Correlation between the survery questions
```{r}
survery_means<-data.frame(Procrastination$DPMean,Procrastination$AIPMean,Procrastination$GPMean,Procrastination$SWLSPMean)
names(survery_means)<-c("DP","AIP","GP","SWLSP")
cor(survery_means)

```
  Looking at the correlation matrix between the survey question variables there is nothing too shocking shown. All there of the question groups that deal with procrastination (DP,AIP,GP) are all highly linearly correlated. This is to be expected because they are all dealing with the procrastination habits of an individual. If they score high on one test it would be expected that they would score high on another test. However something that is very interesting is all of these groups correlation with SWLSP (life satisfaction). All of these correlations are negative. This negative correlation means that if someone has a higher score on one of the procrastination test (meaning they tend to procrastinate) then their life satisfaction decreases. This is a very important connection. This is saying that if you tend to procrastinate you will on average have a lower life satisfaction than if you did not procrastinate. If you think about this relationship it does make sense. People who procrastinate often tend to stress more because they tend to push things off and not complete tasks until right before they are due. It is known that high levels of stress result in not a happy life. This relationship shows that if you want to live a happier life, stop procrastinating. 



