---
title: "Case_Study_Two"
author: "Matt Rega"
date: "November 26, 2017"
output: html_document
runtime: shiny
---

```{r}


#read in data set
library(readr)
library(dplyr)
library(stringi)
library(rvest)
library(xml2)
library(selectr)
library(ggplot2)
library(sqldf)
library(knitr)
library(kableExtra)
library(shiny)
library(rworldmap)

# install.packages("rworldmap")

#setwd("~/SMU/DDS_CS2/Data")
#df = read.csv("Procrastination.csv")
#Procrastination = read.csv("Procrastination.csv")

#kyle 
#I added the lines below anyone can run the RMD file without manually entering their file path into the code
#let me know if this works for you
#MatT can you test this out to see if it works on your machine?
#################################################################
My_FilePath<-getwd()
My_FilePath<-substring(My_FilePath,1,nchar(My_FilePath)-5)
setwd(My_FilePath)
Data_FilePath<-paste( My_FilePath ,"/Data/Procrastination.csv", sep = "")
##################################################################


#setwd("~/SMU/DDS_CS2/Data")
#df = read.csv("Procrastination.csv"))
Procrastination = read.csv(Data_FilePath)
#Procrastination = read.csv("Procrastination.csv")
# Procrastination <- read_csv("C:/Users/student/Desktop/Doing DS/Case_Study_2/Procrastination.csv")

#Print number of rows and columns
dimPro<-dim(Procrastination)
names(dimPro)<-c("Number of Rows", "Number of Columns")
dimPro

#Clean up column names of the data set
ProColNames<-names(Procrastination)

#remove spaces from names
ProColNames<-gsub(" ","",ProColNames[1:length(ProColNames)],fixed = TRUE)

#Age of Participant 
ProColNames[1]<-"Age"

#Current Occupation-->Occupation
ProColNames[7]<-"Occupation"

#How long.....years
ProColNames[8]<-"TenureYears"

#How long...months
ProColNames[9]<-"TenureMonths"

#community size
ProColNames[10]<-"CommSize"

#county of residence
ProColNames[11]<-"Country"

#marital status
ProColNames[12]<-"MaritalStat"

#number of sons/daughters
ProColNames[13]<-"Sons"
ProColNames[14]<-"Daughters"





#all the scale questions 15-59
## Kyle -- I get an error here. I don't think this gets used. When I run grep(")", ProColNames) I get zero results.
##        may want to consider removing this section. 

#original
# for(i in 15:59)
# {
# ProColNames[i]<-substr(ProColNames[i],2,which(strsplit(ProColNames[i],"")[[1]] == ")" )-1)
# }

#based on this it looks like we are trying to split the string to make column names. I propose the below:
#IT does the following:
# replace periods with blanks
# replace â with blanks
# Uses regex to find the first few letters followed by a number in the string
# extract the rest of the string to the first 12 letters of the column name

for (i in 15:59)
{
  ProColNames[i] = gsub("\\.","", ProColNames[i])
  ProColNames[i] = gsub("â","", ProColNames[i])
  holding = stringr::str_locate_all(pattern = "[A-Z\\.]+[0-9]", ProColNames[i])
  ProColNames[i] = substr(ProColNames[i], holding[[1]][2] + 1, 13 + holding[[1]][2])
}

#do you consider yourself.....
ProColNames[60]<-"YouConsider"

#do others ocnsider....
ProColNames[61]<-"OtheConsider"

#Assign names to data set
names(Procrastination)<-ProColNames

#Remove tenure in years that are greater than 100
Procrastination<-Procrastination[-which(Procrastination[8]>100),]

#Change male to 1 and female to 2 in the number of sons column
Procrastination$Sons[which(Procrastination$Sons=="Male")]<-1
Procrastination$Sons[which(Procrastination$Sons=="Female")]<-2

#Remove 0 from country column
Procrastination$Country[Procrastination$Country==0]<-NA

#Remove 0 and please specify from occupation column
Procrastination$Occupation[Procrastination$Occupation==0]<-NA
Procrastination$Occupation[Procrastination$Occupation=="please specify"]<-NA

#Group similar occupations together

#Student
for (i in 1:length(Procrastination$Occupation))
{

if(grepl("student",Procrastination$Occupation[i]))
Procrastination$Occupation[i]<-"Student"

if(grepl("Student",Procrastination$Occupation[i]))
Procrastination$Occupation[i]<-"Student"

}#end for

#teacher
for (i in 1:length(Procrastination$Occupation))
{

if(grepl("teacher",Procrastination$Occupation[i]))
Procrastination$Occupation[i]<-"Teacher"

if(grepl("Teacher",Procrastination$Occupation[i]))
Procrastination$Occupation[i]<-"Teacher"

}#end for

#Manager
for (i in 1:length(Procrastination$Occupation))
{

if(grepl("manager",Procrastination$Occupation[i]))
Procrastination$Occupation[i]<-"Manager"

if(grepl("Manager",Procrastination$Occupation[i]))
Procrastination$Occupation[i]<-"Manager"

}#end for

#Self-Employed
for (i in 1:length(Procrastination$Occupation))
{

if(grepl("self-employed",Procrastination$Occupation[i]))
Procrastination$Occupation[i]<-"Self-Employed"

if(grepl("Self-Employed",Procrastination$Occupation[i]))
Procrastination$Occupation[i]<-"Self-Employed"

}#end for

#Writer
for (i in 1:length(Procrastination$Occupation))
{

if(grepl("Writer",Procrastination$Occupation[i]))
Procrastination$Occupation[i]<-"Writer"

if(grepl("writer",Procrastination$Occupation[i]))
Procrastination$Occupation[i]<-"Writer"

}#end for

#Change columns to correct data types
Procrastination$TenureYears<-round(as.numeric(format(Procrastination$TenureYears,scientific = FALSE),0))
Procrastination$Sons<-as.numeric(Procrastination$Sons)

#Take the mean of the scale questions
Procrastination$DPMean<-round(rowMeans(Procrastination[15:19],na.rm = TRUE),1)
Procrastination$AIPMean<-round(rowMeans(Procrastination[20:34],na.rm = TRUE),1)
Procrastination$GPMean<-round(rowMeans(Procrastination[35:54],na.rm = TRUE),1)
Procrastination$SWLSPMean<-round(rowMeans(Procrastination[55:59],na.rm = TRUE),1)

```


# Question 3: Scrape the Human Development Index (I have added some context to the question to make is seem more like a client request)
Waterfront Data Corp (WDC) is a multinational corporation with offices in countries that are in various stages of development. Knowing this, WDC has asked that the procrastination study take into consideration how developed each country is in which there is an office. 

In order to facilitate this request, we have chosen to bring in Human Development Index (HDI) information for each country. The HDI is used to determine how developed a country is beyond simple economic growth and Gross Domestic Product parameters. Basically, the HDI can be thought of as "a summary measure of average achievement in key dimensions of human development". As such, we believe that HDI data may provide some very interesting insight on procrastination rates on a country by country basis. 

2016 HDI data was gathered from the Human Development Report of the same year. Once the HDI ranking for each country was collected, this data was then merged with the procrastination data set. Then, all people under the age of 18 were removed from the data set at the request of WDC.

```{r q3}
url = "https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index"

page = read_html(url)

#get the table info -- this was for testing
# table = page %>%
#   rvest::html_nodes(xpath = "//td//table") %>%
#   .[1] %>%
#   rvest::html_table(fill = TRUE)

#assing them in a loop
for(i in 1:8) {
  assign(paste0("table", i), as.data.frame(page %>%
  rvest::html_nodes(xpath = "//td//table") %>%
  .[i] %>%
  rvest::html_table(fill = TRUE)
  )
  )
 
}

colnames(table1) = c("2016_Est_Rank", "Rank_Change", "Country", "2016_Est_HDI", "HDI_Change")
colnames(table2) = c("2016_Est_Rank", "Rank_Change", "Country", "2016_Est_HDI", "HDI_Change")
colnames(table3) = c("2016_Est_Rank", "Rank_Change", "Country", "2016_Est_HDI", "HDI_Change")
colnames(table4) = c("2016_Est_Rank", "Rank_Change", "Country", "2016_Est_HDI", "HDI_Change")
colnames(table5) = c("2016_Est_Rank", "Rank_Change", "Country", "2016_Est_HDI", "HDI_Change")
colnames(table6) = c("2016_Est_Rank", "Rank_Change", "Country", "2016_Est_HDI", "HDI_Change")
colnames(table7) = c("2016_Est_Rank", "Rank_Change", "Country", "2016_Est_HDI", "HDI_Change")
colnames(table8) = c("2016_Est_Rank", "Rank_Change", "Country", "2016_Est_HDI", "HDI_Change")

dfHDI = rbind(table1[-1,], table2[-1,], table3[-1,], table4[-1,], table5[-1,], table6[-1,], table7[-1,], table8[-1,])

dfHDI = dfHDI[,c("Country", "2016_Est_HDI")]

dfHDI$HDI_Category = ifelse(dfHDI$`2016_Est_HDI` >= 0.8, "Very High",
                            ifelse(dfHDI$`2016_Est_HDI` >= 0.7, "High",
                                   ifelse(dfHDI$`2016_Est_HDI` >= 0.55, "Medium", "Low")))

##Converts HDI column into numeric for later calculations. 
dfHDI$`2016_Est_HDI`<-as.numeric(dfHDI$`2016_Est_HDI`)

##Make classificaiton of HDI based on score


Procrastination = merge(Procrastination, dfHDI, by = "Country")

```



```{r}

##Removes all individuals under the age of 18 due to legality of none consenting adult. 
Procrastination <- Procrastination[which(Procrastination$Age > 18),]
```

# Descriptive statistics 
Below is some descriptive statistics of the data. The descriptive statistics describe the basic features of the data. 


```{r}
#This function calculates the descriptive statics and puts it into a table 
Descriptive_report<-function(variable){
#Creats objects for caculations
Med.var<-median(variable,na.rm = TRUE)
Min.var<-min(variable,na.rm = TRUE)
Max.var<-max(variable,na.rm = TRUE)
Mean.var<-mean(variable,na.rm = TRUE)
SD.var<-sd(variable,na.rm = TRUE)
Range.var<-Max.var-Min.var

#Puts together objects into one DF and prits with rounding
Report<-data.frame(Min.var,Med.var,Max.var,Mean.var,SD.var,Range.var)
names(Report)<-c("Min","Median","Max","Mean","Standard Deviation","Range")
Report
}
```



###Summary Statistics table
Participants that did not report where excluded from the descriptive statistics calculation.
```{r}

#Labels the variables that will be in the descriptive statistics tables 
Descriptive_Table<-c("Annual.Income","Age","2016_Est_HDI","DPMean","GPMean",
"AIPMean","SWLSPMean")

#Passes "Annual.Income","Age","2016_Est_HDI","DPMean","GPMean",
#"AIPMean","SWLSPMean" variables through the descriptive report function and binds them together into one data frame

Descriptive_Table<-{cbind(Descriptive_Table,rbind(
  Descriptive_report(Procrastination$Annual.Income),
  Descriptive_report(Procrastination$Age),
  Descriptive_report(Procrastination$`2016_Est_HDI`),
  Descriptive_report(Procrastination$DPMean),
  Descriptive_report(Procrastination$GPMean),
  Descriptive_report(Procrastination$AIPMean),
  Descriptive_report(Procrastination$SWLSPMean)))}




```



The histogram of age for participants shows that age is not a normal distribution. Age is skewed to the right. 	

The histogram of Generalized Procrastination (GP) looks to be normally distributed. GP is mean of 5 different questions on the decision procrastination scale. This may make the distribution more bell shaped.


```{r}

hist(Procrastination$Age, 
     main="Histogram of Age",
     xlab= "Age")
hist(Procrastination$GPMean, 
     main="Histogram of Generalized procrastination",
     xlab= "Generalized Procrastination (GP)")

```

###Frequency tables 



```{r} 


####################
#This code block counts the frequency by country, occupation, gender, and work status 
#that appear in the data set. The count is then put into four separate tables that will 
#be used in the shiny app (next code block)
####################


##################### Gender Table ##################################

frequency_Table <-data.frame(count(Procrastination,Procrastination$Gender))
names(frequency_Table)<- c("Gender","Count by Gender")
frequency_Table[,1]<-as.character(frequency_Table[,1])
frequency_Table[which(frequency_Table$Gender==""),1] <- "Not Reported"
GenderTable<-frequency_Table


###################### Work Status Table ##############################

frequency_Table <-data.frame(count(Procrastination,Procrastination$Work.Status))
names(frequency_Table)<- c("Work Status","Count by Work Stauts")
frequency_Table[,1]<-as.character(frequency_Table[,1])
frequency_Table[which(frequency_Table$`Work Status` ==""),1] <- "Not Reported"
WorkStatusTable<-frequency_Table




####################### Occupation Table ############################

frequency_Table <-data.frame(count(Procrastination,Procrastination$Occupation))
names(frequency_Table)<- c("Occupation","Count by Occupation")
frequency_Table[,1]<-as.character(frequency_Table[,1])
frequency_Table[which(frequency_Table$Occupation ==""),1] <- "Not Reported"# Blanks are considered not reported

#Merges the NA's with the Not reported and drops the NA row. 
frequency_Table[which(frequency_Table$Occupation =="Not Reported"),2] <- frequency_Table[which(is.na( frequency_Table$Occupation)),2]+frequency_Table[which(frequency_Table$Occupation =="Not Reported"),2]
frequency_Table <- frequency_Table[which( !is.na( frequency_Table$Occupation)),]

#Arrange Frequency table in descending order and puts it into the Occupation table to be used in the shiny app
Occupation_Table<-arrange(frequency_Table,desc(frequency_Table$`Count by Occupation`))


#Outputs the full occupation list into the data folder 
write.csv(Occupation_Table, file = paste(My_FilePath,"/Data/count_by_Occupation_list.csv",sep = ""),row.names=FALSE)


################################ Country table #####################################

frequency_Table <-data.frame(count(Procrastination,Procrastination$Country))
names(frequency_Table)<- c("Country","Count of Participants by Country")
frequency_Table[,1]<-as.character(frequency_Table[,1])
frequency_Table[which(frequency_Table$Country ==""),1] <- "Not Reported"


CountryTable<-arrange(frequency_Table,desc(frequency_Table$`Count of Participants by Country`))

#Outputs the full occupation list into the data folder 
write.csv(CountryTable, file = paste(My_FilePath,"/Data/count_by_Country_list.csv",sep = ""),row.names=FALSE)


################################# Participant's view Table ##########################

frequency_Table <-data.frame(count(Procrastination[which(
  (Procrastination$YouConsider=="yes" & Procrastination$OtheConsider=="yes")),]))

frequency_Table <-rbind(frequency_Table,data.frame(count(Procrastination[which(
  (Procrastination$YouConsider=="no" & Procrastination$OtheConsider=="no")),])))


frequency_Table<-cbind(c("Participant _and_others_view_as_Procrastinator","Participant _and_others_do_not_view_as_Procrastinator"),frequency_Table)

names(frequency_Table)<-c("View on Procrastination","Count of Participants")

ParticipantTable<- frequency_Table

```
Top 10

```{r}

############################## Shiny App ####################################

#setsup the shiny app envirment 
ui<- fluidPage(
  sliderInput(inputId = "num",label = "Choose number of observations",max = 10,min = 0,
              value = 10),
  radioButtons(inputId = "radTable", label = "Select table to display",
               c("descriptive statistics","Occupation","Country","Work Status","Gender", 
                 "Participant's views on Procrastination"), 
               selected = "descriptive statistics"),
  
  tableOutput("ShinyTable")

  )

#Function that will manipulate the table based on the input from the slider bar   
server<-function(input,output,session){
  output$ShinyTable<- renderTable({
    radTable<-switch(input$radTable,
                     Occupation = Occupation_Table,
                     Country = CountryTable,
                     Gender = GenderTable,
                     'Work Status' = WorkStatusTable,
                     "Participant's views on Procrastination" = ParticipantTable,
                     'descriptive statistics' = Descriptive_Table)
    
    updateSliderInput(session,"num",max = length(radTable[,1]))
    
    head(radTable,input$num)
    
  })
  
}
#Designated sever to run on 
shinyApp(ui=ui, server=server)



```


# Question 5B and 5C

WDC wanted to know which countries had the highest average General Procrastination and Decisional Procrastination score. The best way to show this data is with some bar charts. Below, there are two bar charts that depict this information. Scores are sorted form highest to lowest and the color of each bar is indicative of the HDI score of the respective country. Of the top 15 countries in each category, 9 of them appeared in both charts. The countries that appear in both charts are listed below.

To provide more context for WDC, world maps were plotted and the HDI, Mean General Procrastination Score, and Mean Decisional Procrastination Score. All other countries are shown as grey. Finally, we have also plotted on the world map where the top 15 most procrastinating countries are located. What is interesting about this view is that there appears to be a clusering effect in Europe and the Middle East.
```{r}
#Q5B Barchart
countryGPmean = aggregate(GPMean ~ Country + HDI_Category, Procrastination, mean)
sortedGP = countryGPmean[order(countryGPmean$GPMean, decreasing = TRUE),][1:15,]


ggplot(data=sortedGP, aes(x= reorder(Country, -GPMean), y = GPMean, fill = HDI_Category)) + 
  geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90)) + 
  xlab("Country") + 
  ylab("Mean General Procrastination Score") + 
  ggtitle("Top 15 Countries by Average General Procrastination Scale") + 
  scale_fill_brewer(palette = "Dark2")


#Q5C Barchart
countryDPmean = aggregate(DPMean ~ Country + HDI_Category, Procrastination, mean)
sortedDP = countryDPmean[order(countryDPmean$DPMean, decreasing = TRUE),][1:15,]

ggplot(data=sortedDP, aes(x= reorder(Country, -DPMean), y = DPMean, fill = HDI_Category)) + 
  geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90)) + 
  xlab("Country") + 
  ylab("Mean Devisional Procrastination Score") + 
  ggtitle("Top 15 Countries by Average Decisional Procrastination Scale") + 
  scale_fill_brewer(palette = "Dark2")

#Which countries are in both charts

inBoth = sqldf('SELECT Country FROM sortedDP INTERSECT SELECT Country from sortedGP')
paste0("There are ", count(inBoth), " countries that show up in the top 15 countries for GP and DP Score. They are:")
inBoth

############################# World Mapping ###########################
######## Glocal HDI Chart ########
mapped_procrast = joinCountryData2Map(Procrastination, joinCode = "NAME", nameJoinColumn = "Country")
par(mai=c(0,0,0.2,0),xaxs="i",yaxs="i")
mapCountryData(mapped_procrast, nameColumnToPlot = "HDI_Category", colourPalette = "rainbow", mapRegion = "world", numCats = 5, catMethod = "categorical", mapTitle = "HDI by Country where WDC has an Office", missingCountryCol = "grey")

#### Mean GP Procrastination Scores for All Countries####
mapped_gp = joinCountryData2Map(countryGPmean, joinCode = "NAME", nameJoinColumn = "Country")
par(mai=c(0,0,0.2,0),xaxs="i",yaxs="i")
mapCountryData(mapped_gp, nameColumnToPlot = "GPMean", colourPalette = "heat", mapRegion = "world", mapTitle = "Mean GP Score by Country where WDC has an Office", missingCountryCol = "grey")

#### Mean DP Procrastination Scores for All Countries####
mapped_dp = joinCountryData2Map(countryDPmean, joinCode = "NAME", nameJoinColumn = "Country")
par(mai=c(0,0,0.2,0),xaxs="i",yaxs="i")
mapCountryData(mapped_dp, nameColumnToPlot = "DPMean", colourPalette = "heat", mapRegion = "world", mapTitle = "Mean DP Score by Country where WDC has an Office", missingCountryCol = "grey")

### Top 15 GP Sore by Country ###
gp15 = joinCountryData2Map(sortedGP, joinCode = "NAME", nameJoinColumn = "Country")
par(mai=c(0,0,0.2,0),xaxs="i",yaxs="i")
mapCountryData(gp15, nameColumnToPlot = "GPMean", colourPalette = "heat", mapRegion = "world", mapTitle = "Top 15 Countries with Highest Mean GP Score", missingCountryCol = "grey")

### Top 15 DP by Country ###
dp15 = joinCountryData2Map(sortedDP, joinCode = "NAME", nameJoinColumn = "Country")
par(mai=c(0,0,0.2,0),xaxs="i",yaxs="i")
mapCountryData(dp15, nameColumnToPlot = "DPMean", colourPalette = "heat", mapRegion = "world", mapTitle = "Top 15 Countries with Highest DP Score", missingCountryCol = "grey")

```


#Relationship between Income and Age
```{r}
#Scatterplot
ggplot(subset(Procrastination,!is.na(AnnualIncome)&!is.na(Age)&!is.na(Gender)),aes(x=Age,y=AnnualIncome,shape=Gender,color=Gender))+geom_point()+xlab("Age")+ylab("Annual Income in Dollars")+ggtitle("Annual Income vs Age")+theme(plot.title = element_text(hjust=0.5))

#create smaller data set for regression model
income_age_data<-data.frame(Procrastination$Age,Procrastination$Gender,Procrastination$AnnualIncome)
names(income_age_data)<-c("Age","Gender","Income")
income_age_data$male<-ifelse(income_age_data$Gender=="Male",1,0)

#correlation of age and income
cor.test(Procrastination$Age,Procrastination$AnnualIncome,method="pearson",use = "complete.obs")

#create linear regression model using just age 
income_age_model<-lm(Income~Age,data=income_age_data)
summary(income_age_model)

#create linear regression model using age and gender
income_age_model2<-lm(Income~male+Age,data=income_age_data)
summary(income_age_model2)

```

	Overall there is a statistically significant linear relationship between a person's age and their annual income. The scatter plot is a little challenging to read because there are so many observations with the same age and income but the correlation test can be used to interpret this relationship. The correlation coefficient is 0.3723 with a p-value of less than 0.05. This means that the two variable are linear correlated and since 0.3723 is positive they are positively correlated. As age increases so does annual income. This is not a particularly strong correlation but there is one present.
	This relationship is further supported by looking at a simple linear regression occasion using age to predict annual income. The coefficient for age is 1498.12 which means that for every one year increase in age a person's annual income is predicted to increase by $1,498.12. Again this is an increase which supports the positive linear correlation found using the correlation test.
	If we add gender into the regression equation the coefficient for age drops to 1458.2. This means that for every one year increase in age a person's annual income is predicted to increase $1,458.2. The coefficient for the male indicator variable, this variable has a value of 1 if the observation is a male, is 15859. This means that if a male and female are the same age it is predicted that the male would have an annual income that is $15,859 higher than the female.  

#Relationship between Life Satisfaction and Human Development Index
```{r}
#scatterplot life satisfaction vs hdi
ggplot(Procrastination,aes(x=Procrastination$`2016_Est_HDI`,y=SWLSPMean,shape=Gender,color=Gender))+geom_point()+xlab("Human Development Rating")+ylab("Life Statisfaction Rating (1-5(Highest))")+ggtitle("Life Statisfaction vs Human Development Rating")+theme(plot.title = element_text(hjust=0.5))+scale_x_discrete(breaks=pretty(Procrastination$`2016_Est_HDI`,n=75))+coord_flip()

#create smaller data set for regression model
ls_hdi_data<-data.frame(as.numeric(Procrastination$`2016_Est_HDI`),Procrastination$Gender,Procrastination$SWLSPMean)
names(ls_hdi_data)<-c("HDI","Gender","Life_Satisfaction")
ls_hdi_data$male<-ifelse(ls_hdi_data$Gender=="Male",1,0)

#correlation of HDI and Life satisfaction
cor.test(as.numeric(Procrastination$`2016_Est_HDI`),Procrastination$SWLSPMean,method="pearson",use = "complete.obs")

#create linear regression model using just HDI to predict life satisfaction
ls_hdi_model<-lm(Life_Satisfaction~HDI,data=ls_hdi_data)
summary(ls_hdi_model)

#Create linear regression model using HDI and gender to predict life satisfaction
ls_hdi_model2<-lm(Life_Satisfaction~HDI+male,data=ls_hdi_data)
summary(ls_hdi_model2)

```
  Again the scatterplot is difficult to read due to the high number of similar observations so we will look at the statistical tests. The correlation test returns a correlation coefficient of 0.0395 with a p-value of 0.01. This means that human development index and life satisfaction do have a statistically significant linear relationship but it is very weak. The correlation coefficient is only 0.03 so the relation is not strong. It is positive though which means that as the human development index of the country goes up the life satisfaction of the observation increases as well, even if it is only slightly.
	This again is supported by a linear regression model. First looking at only using the human development index to predict an observations predicted life satisfaction. The coefficient for HDI is 0.6855 which means for a 0.1 unit increase in HDI an observations life satisfaction only increases by 0.06855. We use 0.1 increase for HDI because it is measured on a scale from 0 to 1 so a 1 unit increase is extremely unlikely and a 0.1 unit increase is much more plausible. Life satisfaction is measured on a scale from 1 to 5 so a 0.06 unit increase is not nothing but it is not a large increase. This supports the correlation coefficient being very weak.
	If we include gender in the regression equation, again with an indicator variable that equals 1 if the observation is a male, the coefficient for HDI drops to 0.51255 which means that now a 0.1 unit increase in HDI results in a predicted increase of 0.05 in life satisfaction. The coefficient for the male indicator variable is -0.235. This means that if a male and female lived in a country with the same HDI the male would have a life expectance 0.235 units lower than the female. This suggests that men are on average less satisfied than females.

#Relationship between life satisfaction and hdi category
```{r}
#Create a barplot of life statisfaction and hid category
hdi_ls_mean<-aggregate(Procrastination$SWLSPMean,list(Procrastination$HDI_Category),mean)
names(hdi_ls_mean)<-c("Group","Mean_Life_Satisfaction")

ggplot(hdi_ls_mean,aes(x=reorder(Group,Mean_Life_Satisfaction),y=Mean_Life_Satisfaction))+geom_bar(stat="identity",fill="#009E73")+ggtitle("Mean Life Satisfaction by HDI Category")+theme(plot.title = element_text(hjust=0.5))+xlab("HDI Category")+ylab("Mean Life Satisfaction")

#Anova test comparing the four groups
anova_model<-aov(Procrastination$SWLSPMean~Procrastination$HDI_Category)
summary(model)
TukeyHSD(model)
```
  Looking at the bar graph there does seem to be an increase in life satisfaction as the HDI category moves to a higher quality of life. However if an ANOVA test is run on the different groups this says the opposite. The ANOVA test has a p-value of 0.128 which means that the four groups do not have statistically significant different life satisfaction ratings. So while it does look like there is an increase in life satisfaction this increase is not statistically significant.
  
#Correlation between the survery questions
```{r}
survery_means<-data.frame(Procrastination$DPMean,Procrastination$AIPMean,Procrastination$GPMean,Procrastination$SWLSPMean)
names(survery_means)<-c("DP","AIP","GP","SWLSP")
cor(survery_means)

```
  Looking at the correlation matrix between the survey question variables there is nothing too shocking shown. All there of the question groups that deal with procrastination (DP,AIP,GP) are all highly linearly correlated. This is to be expected because they are all dealing with the procrastination habits of an individual. If they score high on one test it would be expected that they would score high on another test. However something that is very interesting is all of these groups correlation with SWLSP (life satisfaction). All of these correlations are negative. This negative correlation means that if someone has a higher score on one of the procrastination test (meaning they tend to procrastinate) then their life satisfaction decreases. This is a very important connection. This is saying that if you tend to procrastinate you will on average have a lower life satisfaction than if you did not procrastinate. If you think about this relationship it does make sense. People who procrastinate often tend to stress more because they tend to push things off and not complete tasks until right before they are due. It is known that high levels of stress result in not a happy life. This relationship shows that if you want to live a happier life, stop procrastinating. 